\begin{resumo}[Abstract]
 \begin{otherlanguage*}{english}
   In an increasingly connected world, technology is an invaluable ally in promoting culture and the arts. In this sense, the Casa de Cultura de Monlevade has sought new ways to foster local artistic talent, and the development of a platform for artists from Monlevade is an initiative that has stood out in this scenario. It should be noted that in the city of João Monlevade, the Casa de Cultura fulfills the role of Municipal Secretary of Culture. The problem that this work intends to contribute to the solution is a demand pointed out by the current Coordinator of the Casa de Cultura who sought partnerships at Ufop for the development of solutions. Given this context, it is clear that the development of the Monlevade artists' platform is an important step towards strengthening the local cultural scene. For Raman & Bansal (2014, p. 15): "A portal for art and artists can play an important role in promoting local culture and creating a space for the exhibition and sale of works of art, in addition to providing information about cultural events in the region.”, and it is with this objective in mind that Casa de Cultura has been working, seeking partnerships and resources to make this idea a reality.

   \vspace{\onelineskip}

   \noindent
   \textbf{Key-words}: Artist platform.
     Cultural platform development.
     House of Culture.
     Monlevadese artists.
     Cultural management.
     Creative economy.
     Technology in culture.
     Cultural marketing.
     Cultural entrepreneurship.
     Promotion of local artists.
 \end{otherlanguage*}
\end{resumo}